Global code motion of congruent instructions

### 2017-04-18 paper.tex
typos

Spills are listed in Table~\ref{tab:spills}. Spills were reduced by an average
of 2\% on the \SPEC{} benchmark suite. This is a result of cost-model which
limits the \gcm{} to those candidates which do not increase the register
pressure (except for loads Section~\ref{subsec:cost-models}, overall spills
still decreases.

@@

The compilation time actually reduced for most of the benchmarks as a result of code motion.
This is because, as \gcm{} removes (congruent) instructions, the number of instructions
to be processed by later compilation passes also reduces. The compilation time listed here
is the total instruction count as outputted from valgrind (--tool=cachegrind) \cite{valgrind}.

>>>>

Spills are listed in Table~\ref{tab:spills}. Spills were reduced by an average
of 2\% on the \SPEC{} benchmark suite. This is a result of cost-model which
limits the \gcm{} to those candidates which do not increase the register
pressure (except for loads Section~\ref{subsec:cost-models},) overall spills
still decreases.

@@

The compilation time actually reduced for most of the benchmarks as a result of code motion.
This is because, as \gcm{} removes (congruent) instructions, the number of instructions
to be processed by later compilation passes also reduces. The compilation time listed here
is the total instruction count as outputted from valgrind -{}-tool=cachegrind \cite{valgrind}.
